Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-07-31 manuscript/04-results.Rmd
Updated paper

``` {r, biophysical-model, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE}
library(lme4)
library(AICcmodavg) #aictab function
library(car)
library(piecewiseSEM)
library(data.table)
library(knitr)
library(kableExtra)

>>>>

``` {r, biophysical-model, eval=TRUE, echo=FALSE, message=FALSE}
library(lme4)
library(AICcmodavg) #aictab function
library(car)
library(piecewiseSEM)
library(data.table)
library(knitr)
library(kableExtra)
